Differentiable Neural Computers

### 2018-05-25 Presentation/Presentation.tex
changes according to feedback

		% core nodes
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
			at (-0,6) {\textcolor{black}{$;$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (s) 
			at (9,6) {\large\textcolor{black}{$\Cc_t^l$}};
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (fx) 
			at (9,4) {\textcolor{black}{$\times$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (f) 
			at (9,2) {\large\textcolor{black}{$\ff_t^l$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (i) 
			at (6,8) {\large\textcolor{black}{$\ii_t^l$}};
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (ix) 
			at (6,6) {\textcolor{black}{$\times$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (id) 
			at (4,8) {\textcolor{black}{$\zeta_i$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (sd) 
			at  (4,6) {\small\textcolor{black}{$\zeta_c$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (o) 
			at (16,10) {\large\textcolor{black}{$\oo_t^l$}};
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (ox) 
			at (16,6) {\textcolor{black}{$\times$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (hd) 
			at (12,6) {\small\textcolor{black}{$\zeta_h$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (odd) 
			at (4,10) {\small\textcolor{black}{$\zeta_o$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (fd) 
			at (4,2) {\small\textcolor{black}{$\zeta_f$}};
		% recurrency
		\draw (f) edge[thick] (fd);
		\draw[thick] (fd) -| (2,6);
		\draw[thick] (2,6) |- (odd);
		\draw (odd) edge[->,thick] (o);
		\draw[thick] (2,6) |- (id);
		\draw (id) edge[thick] (i);
		% gates
		\draw (o) edge[->, thick] (ox);
		\draw (i) edge[->, thick] (ix);
		\draw (s) edge[->,bend right=45, thick, densely dotted, gray!90] (fx);
		\draw (s) edge[<-,bend left=45, thick] (fx);
		\draw (f) edge[->, thick] (fx);
		% forward
		\draw (-2,4)[->,thick] -| (conc);
		\draw(-2,6) edge[thick,->] (conc);
		\draw (0,6) edge[thick] (sd);
		\draw (sd) edge[->, thick] (ix);
		\draw (ix) edge[->, thick] (s);
		\draw (s) edge[thick] (hd);
		\draw (hd) edge[->, thick] (ox);
		\draw (ox) edge[->, thick] (20,6);

@@

\begin{frame}{Conclusion}
	\alert{Recap}\\
	\begin{itemize}
	\item We can simulate computation and expand upon it by using differentiable, continuous operations.\\
	\item[] We can automatically infer simple functions over complex data structures in the form of \alert{probability distributions}, just by using examples!\\
	\end{itemize}
\end{frame}

>>>>

		% core nodes
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
			at (-0,6) {\textcolor{black}{$;$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (s) 
			at (9,6) {\large\textcolor{black}{$\Cc_t^l$}};
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (fx) 
			at (9,4) {\textcolor{black}{$\times$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (f) 
			at (9,2) {\large\textcolor{black}{$\ff_t^l$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (i) 
			at (6,8) {\large\textcolor{black}{$\ii_t^l$}};
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (ix) 
			at (6,6) {\textcolor{black}{$\times$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=gray!70] (id) 
			at (4,8) {\textcolor{black}{$\zeta_i$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=gray!70] (sd) 
			at  (4,6) {\small\textcolor{black}{$\zeta_c$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (o) 
			at (16,10) {\large\textcolor{black}{$\oo_t^l$}};
		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (ox) 
			at (16,6) {\textcolor{black}{$\times$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=gray!70] (hd) 
			at (12,6) {\small\textcolor{black}{$\zeta_h$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=gray!70] (odd) 
			at (4,10) {\small\textcolor{black}{$\zeta_o$}};
		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=gray!70] (fd) 
			at (4,2) {\small\textcolor{black}{$\zeta_f$}};
		% recurrency
		\draw (f) edge[thick] (fd);
		\draw[thick] (fd) -| (2,6);
		\draw[thick] (2,6) |- (odd);
		\draw (odd) edge[->,thick] (o);
		\draw[thick] (2,6) |- (id);
		\draw (id) edge[thick] (i);
		% gates
		\draw (o) edge[->, thick] (ox);
		\draw (i) edge[->, thick] (ix);
		\draw (s) edge[->,bend right=45, thick, densely dotted, gray!90] (fx);
		\draw (s) edge[<-,bend left=45, thick] (fx);
		\draw (f) edge[->, thick] (fx);
		% forward
		\draw (-2,4)[->,thick] -| (conc);
		\draw(-2,6) edge[thick,->] (conc);
		\draw (0,6) edge[thick] (sd);
		\draw (sd) edge[->, thick] (ix);
		\draw (ix) edge[->, thick] (s);
		\draw (s) edge[thick] (hd);
		\draw (hd) edge[->, thick] (ox);
		\draw (ox) edge[->, thick] (20,6);

@@

\begin{frame}{Conclusion}
	\alert{Recap}\\
	\begin{itemize}
	\item We can simulate computation and expand upon it by using differentiable, continuous operations.\\
	\item Simple programs (over complex data structures) can now be automagically inferred.\\
	\end{itemize}
\end{frame}
